### 2022-08-24 ersteops/templates/printpdf/paperless_template.tex
update template

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%

    %Folio
    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.id}}\end{tabular}}}}%

    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%

    %Paciente
    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_phone}}\end{tabular}}}}%
    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%

    %Paciente desconocido
    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_unknow}}\end{tabular}}}}%
    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%

    %Padecimiento
    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_current_condition}}\end{tabular}}}}%
    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%

    %Generales
    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.attention_place}} \end{tabular}}}}%
    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_type}} \end{tabular}}}}%
    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.event_type}} \end{tabular}}}}%
    %Trauma
    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_traumatics %}{{ item }},{% endfor %}\end{tabular}}}}%
    %Ojo Izquierdo
    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
    %Ojo Derecho
    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_consultation_reason %}{{ item }},{% endfor%}
    \end{tabular}}}}%
    %to_fix
    %Via Aerea
    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{% for item in content.json_airway %}\fontfamily{lmss}\selectfont\scriptsize {{ item.airway_type}} - {{ item.instruction }}\\{% endfor %}\end{tabular}}}}%

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ content.medications }}\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_medications %}{{ item.medication_type }} - {{ item.medication_name }} - {{ item.medication_hrs }} hrs\\{% endfor %}\end{tabular}}}}%

    %Antecedentes
    %Diabetes
    \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_daibetes_melitus}}\end{tabular}}}}%
    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_daibetes_melitus}}\end{tabular}}}}%
    %Hipertension
    \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_arterial_hypertension}}\end{tabular}}}}%
    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_arterial_hypertension}}\end{tabular}}}}%
    %Cardiopatias
    \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
    \put(0.63928128,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_heart_disease}} \end{tabular}}}}%
    \put(0.59572153,0.48073243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_heart_disease}} \end{tabular}}}}%        
    %Neumopatias
    \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
    \put(0.63928128,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_pneumopathies}}\end{tabular}}}}%
    \put(0.59572153,0.45747395){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_pneumopathies}}\end{tabular}}}}%
    %Trauma
    \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
    \put(0.63928128,0.43527803){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_trauma}}\end{tabular}}}}%
    \put(0.59572153,0.43421546){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_trauma}}\end{tabular}}}}%
    %Alergy
    \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
    \put(0.63928128,0.41201958){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_alergy}}\end{tabular}}}}%
    \put(0.59572153,0.410957){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_alergy}}\end{tabular}}}}%
    %Other
    \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
    \put(0.63928128,0.38876109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.other_pathological_history}}\end{tabular}}}}%
    %\put(0.59572153,0.38769855){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

>>>>

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{master_parte_medico}}%
    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
    %Times
    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.emergency_created_at}}\end{tabular}}}}%
    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.unit_dispatched_time}}\end{tabular}}}}%
    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.arrival_time}}\end{tabular}}}}%
    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.attention_time}}\end{tabular}}}}%
    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.final_emergency_time}}\end{tabular}}}}%

    {% if content.attention_final_grade == 'G0' %}
    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
    {% endif %}
    {% if content.attention_final_grade == 'G1' %}
    \put(0.42545332,0.57475133){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
    {% endif %}
    {% if content.attention_final_grade == 'G2' %}
    \put(0.4811341,0.5742217){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
    {% endif %}
    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.id}}\end{tabular}}}}%

    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_code}}\end{tabular}}}}%
    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit}}\end{tabular}}}}%
   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_type}}\end{tabular}}}}%
    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_plate}}\end{tabular}}}}%

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.erste_code}} - {{content.odoo_client_name}}\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_phone}}\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_gender}}\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_age}}\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_name}}\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_address}}\end{tabular}}}}%

    %Paciente desconocido
    \put(0.23723674,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_unknow}}\end{tabular}}}}%
    \put(0.07146203,0.50540156){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  {{content.patient_affiliations}}\end{tabular}}}}%
    \put(0.07920229,0.49404644){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_clothes}}\end{tabular}}}}%
    \put(0.37437746,0.49499384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.skin_color}}\end{tabular}}}}%

    %Padecimiento
    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_current_condition}}\end{tabular}}}}%
    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%

    %Generales
    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.attention_place}} \end{tabular}}}}%
    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_type}} \end{tabular}}}}%
    {% if content.event_type == 'Traumaticos'%}
      \put(0.30180123,0.46556814){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
    {% else %}
      \put(0.3007691,0.47620579){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
    {% endif%}
    %Trauma
    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_traumatics %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor %}\end{tabular}}}}%
    %Ojo Izquierdo
    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
    %Ojo Derecho
    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_consultation_reason %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
    \end{tabular}}}}%
    %to_fix
    %Via Aerea
    \put(0.32505266,0.47551987){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{% for item in content.json_airway %}\fontfamily{lmss}\selectfont\scriptsize {{ item.airway_type}} - {{ item.instruction }}\\{% endfor %}\end{tabular}}}}%

    {% for item in content.json_pupil_state_left%}
      {% if item == 'Isocoria'%}
        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Midriasis'%}
        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Miosis'%}
        \put(0.4335137,0.38189188){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Anisocoria'%}    
        \put(0.43399571,0.35447078){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
    {% endfor %}
    {% for item in content.json_pupil_state_right %}
      {% if item == 'Isocoria'%}
        \put(0.45563683,0.44651401){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Midriasis'%}
        \put(0.45601685,0.41487724){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Miosis'%}
        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
      {% if item == 'Anisocoria'%}  
        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
      {% endif %}
    {% endfor%}

    %inmovilizacion
    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}{% for item in content.json_inmovilization_type %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
    \end{tabular}}}}%

    %Impresion diagnostica
    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
    %Tratamiento
    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ content.medications }}\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_medications %}{{ item.medication_type }} - {{ item.medication_name }} - {{ item.medication_hrs }} hrs\\{% endfor %}\end{tabular}}}}%

    %Antecedentes
    %Diabetes
    %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_daibetes_melitus}}\end{tabular}}}}%
    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_daibetes_melitus}}\end{tabular}}}}%

    % %Hipertension
    % \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
    \put(0.11758108,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_arterial_hypertension}}\end{tabular}}}}%
    \put(0.14099679,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_arterial_hypertension}}\end{tabular}}}}%
